Logarithmic Space Verifiers on NP-complete

### 2019-11-15 doc/manuscript.tex
Updated amazing result

\section{Preliminaries}

@@

\begin{definition}
The class $1LNL$ contains those languages that are decided by a nondeterministic one-way logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves deterministically on $y$ and nondeterministically on $z$.
\end{definition}

\begin{theorem}
\label{partially}
$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
\end{theorem}

\begin{proof}
On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string. On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$. Hence, we can create the languages $L''' \in 1LNL$ such that
\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation. In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$. However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$. Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
\end{proof}

Now, we define two classes defined under $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.

\begin{definition}
The class $2L$ contains those languages that are deterministic logarithmic space reduced to a language in $1L$. The class $2NL$ consists in those languages that are nondeterministic logarithmic space reduced to a language in $1NL$.
\end{definition}

@@

\begin{proof}
We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively. Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.

On the one hand, every language $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@

\section{Programming Codes}

>>>>

\section{Theory and Methods}

\subsection{Preliminaries}

@@

\begin{definition}
\label{definition}
The class $LNL$ contains those languages that are decided by a nondeterministic logarithmic space Turing machine $N$ such that for every instance $x = yz$ of these languages, there are a prefix and suffix substrings $y$ and $z$ where $N$ moves strictly deterministically on $y$ and strictly nondeterministically on $z$ while strictly deterministically means there is no a possible nondeterministic step and strictly nondeterministically means there is at least one nondeterministic step.
\end{definition}

Sauerhoff have shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input (``nondeterminism at the beginning") \cite{MS03}.

@@

\begin{proof}
We have that $NL \subseteq LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Certainly, the languages in the class $L \subseteq NL$ could be decided by nondeterministic logarithmic space Turing machines that exactly do a single nondeterministic step after the original acceptance state choosing nondeterministically the same acceptance state within two equals choices from the original and modified deterministic logarithmic space Turing machines which decide these languages (this is assuming the prefix string $y$ is the empty string in the instances $x = yz$). Moreover, we have that $LNL \subseteq NL$, because the languages in $LNL$ are decided by nondeterministic logarithmic space Turing machines. Since $NL \subseteq LNL$ and $LNL \subseteq NL$, then the complexity class $LNL$ is equal to $NL$. However, we can state that $BNL \neq LNL$, because there is no possible way for an instance $x = yz$ when the prefix $y$ is the empty string in some languages in $BNL$, such that we could move strictly nondeterministically on $y$ (that would be a ``nondeterminism at the beginning") and move strictly deterministically on the nonempty string $z$ over the Definition \ref{definition} of $LNL$. Hence, we obtain that $BNL \neq NL$ by transitivity. Nevertheless, Sauerhoff have also shown that $L \subseteq BNL \subseteq NL$ \cite{MS03}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@

\subsection{Codes}
